---
title: "Basic1"
author: "Minji Kim"
date: '2020 7 14 '
output: html_document
---

```{r echo=T, results='hide'}
## Install packages
#install.packages("tm")
#install.packages("wordcloud")
#install.packages("ggplot2")

## Load packages
library(tm)
library(wordcloud)
library(ggplot2)
```


## 1 : 텍스트 시각화
```{r}
################################################################################
########################## 1. 그림을 이용한 요약
################################################################################


letters; LETTERS
seq(1,1000,len = 62)
wordcloud(c(letters, LETTERS, 0:9),seq(1, 1000, len = 62))
```
## 2 : 텍스트 시각화

```{r}

data(crude)
wordcloud(crude)
```
## 3 : scatter plot (산점도)
```{r}
data(iris)
ggplot() + geom_point(data=iris, aes(x=Sepal.Length, y=Sepal.Width) ) + xlab ('sepal length') + ylab('sepal width') + ggtitle("Iris")+ theme(plot.title = element_text(hjust = 0.5)) 
```


geom_line generates line geometries.

```{r}
## 4 : scatter plot (conti.)
ggplot() + geom_point(data=iris, aes(x=Sepal.Length, y=Sepal.Width), shape = 3, color='red', cex=2) + xlab ('sepal length') + ylab('sepal width') + ggtitle("Iris")+ theme(plot.title = element_text(hjust = 0.5)) 

ggplot() + geom_line(data=iris, aes(x=Sepal.Length, y=Sepal.Width)) + xlab ('sepal length') + ylab('sepal width') + ggtitle("Iris")+ theme(plot.title = element_text(hjust = 0.5)) 

```
```{r}
head(colors(),20)

```

A violin plot is a symmetrical version of a density plot which provides greater detail of a sample’s distribution than a boxplot.

```{r}
## 5 : scatter plot (conti.)

ggplot() + geom_violin(data=iris, aes(x="", y=Sepal.Width), fill="pink") + ylab('sepal width') + ggtitle("Iris")+ theme(plot.title = element_text(hjust = 0.5))

ggplot(iris, aes(x = Sepal.Width)) + geom_histogram(fill = "tomato") 
```

```{r}
## 6 : scatter plot (conti.)
ggplot() + geom_point(data=iris, aes(x=Sepal.Length, y=Sepal.Width)) + xlab ('length') + ylab('width') + ggtitle("Iris")+ theme(plot.title = element_text(hjust = 0.5)) +
   geom_point(data=iris, aes(x=Petal.Length, y=Petal.Width), shape = 3, color='tomato', cex=3)

```
```{r}
## 7 : scatter plot (conti.)
x <- seq(0, 2*pi, 0.1)
y <- sin(x)
y2 <- sin(3*seq(0, 2*pi, 0.1))
plot(x, y)
lines(x, y, col="purple")
lines(x, y2, col="orange")
```
```{r}
## 8 : scatter plot (conti.)
plot(iris$Sepal.Length,iris$Sepal.Width, xlab="sepal length", 
     ylab="sepal width", main="Iris")
text(iris$Sepal.Length,iris$Sepal.Width, pos=2, cex=0.5 )


ggplot(iris, aes(x=Sepal.Length, y=Sepal.Width) )  +geom_point(pch='+')+ xlab ('sepal length') + ylab('sepal width') + ggtitle("Iris")+ 
   theme(plot.title = element_text(hjust = 0.5))  + geom_text( aes(label = rownames(iris)))

```

```{r}
## 9 : scatter plot (conti.)
plot(iris$Sepal.Length , iris$Sepal.Width , cex=1.5, pch=20, 
     xlab="length", ylab="width", main="Iris")

points(iris$Petal.Length , iris$Petal.Width , cex=1.5, pch="+", 
       col="tomato")  # or pch="43" does same

legend("topright", legend=c("Sepal", "Petal"), pch=c(20, 43), 
       col=c("black", "tomato"), bg="white")

ggplot() + geom_point(data=iris, aes(x=Sepal.Length, y=Sepal.Width, colour = 'sepal')) + xlab ('length') + ylab('width') + ggtitle("Iris")+ theme(plot.title = element_text(hjust = 0.5)) +
   geom_point(data=iris, aes(x=Petal.Length, y=Petal.Width, colour='petal'), shape = 3, cex=3) 

```

https://stackoverflow.com/questions/3735286/create-a-matrix-of-scatterplots-pairs-equivalent-in-ggplot2
```{r}
## 10 : scatter plot (conti.)
pairs(~Sepal.Width + Sepal.Length + Petal.Width + Petal.Length, 
      data=iris, col=c("red", "green", "blue")[iris$Species])
```

## 11 : bar plot (막대그림)
```{r}
barplot(tapply(iris$Sepal.Width,iris$Species,mean))
```

## 12 : 연속형 자료의 이산형 자료로의 변환
```{r}
partition <- cut(iris$Sepal.Width , breaks=10) 
head(partition,3)

table(partition)    
```

## 13 : pie chart (원도표)
```{r}
pie(table(cut(iris$Sepal.Width , breaks=10)), cex=1.5)
```

## 14 : histogram (히스토그램)
```{r}
hist(iris$Sepal.Width)
```
```{r}
## 15 : histogram (conti.)
par(mfrow=c(1,2))

hist(iris$Sepal.Width,breaks=20)

hist(iris$Sepal.Width,freq=FALSE)

ggplot(iris, aes(x = Sepal.Width)) + geom_histogram(binwidth = .5) 
```

## 16 : histograrm (density plot)
```{r}
par(mfrow=c(1,2))

plot(density(iris$Sepal.Width))

hist(iris$Sepal.Width,freq=FALSE)

lines(density(iris$Sepal.Width),col='rosybrown')

ggplot(data=iris, aes(x=Sepal.Width))+ geom_histogram(binwidth=0.2, color="black", fill="steelblue", aes(y=..density..)) +
  geom_density(stat="density", alpha=I(0.2), fill="blue") +
  xlab("Sepal Width") +  ylab("Density") + ggtitle("Histogram & Density Curve")
```

## 17 : scatter plot (산점도)
```{r}
dev.off()

plot(faithful$eruptions,faithful$waiting,xlab='Eruptions',
     ylab='Waiting',cex.lab=2,cex.axis=1)
```

## 18 : scatter plot (Species로 구분하여 plotting)
```{r}
plot(iris$Petal.Length,iris$Petal.Width,xlab='Petal.Length',
     ylab='Petal.Width',cex.lab=2,cex.axis=2,type='n',cex=2)

# iris$Species=='setosa'
# iris$Petal.Length[iris$Species=='setosa']

# setosa 점찍기
points(iris$Petal.Length[iris$Species=='setosa'],
       iris$Petal.Width[iris$Species=='setosa'],col='red')

# versicolor 점찍기
points(iris$Petal.Length[iris$Species=='versicolor'],
       iris$Petal.Width[iris$Species=='versicolor'],col='blue')

# virginical 점찍기
points(iris$Petal.Length[iris$Species=='virginica'],
       iris$Petal.Width[iris$Species=='virginica'],col='green')

ggplot(iris, aes(x=Petal.Length, y=Petal.Width, colour=Species))+geom_point()

```

## 19 : 중심 측도 (평균, 중앙값, 최대값)
```{r}
################################################################################
########################3# 수치를 이용한 요약
################################################################################

length(faithful$waiting)

mean(faithful$waiting)

median(faithful$waiting)

freq=tabulate(faithful$waiting)

tabulate(c(2,3,3,5))

max(freq)

which.max(freq)
```

## 20 : 산포 (분산, 표준편차)
```{r}
n=length(faithful$eruptions)

sum((faithful$eruptions - mean(faithful$eruptions))^2)/(n-1) 

var(faithful$eruptions) 

sqrt(var(faithful$eruptions))

sd(faithful$eruptions) 
```

## 21 : 산포 (IQR, 범위)
```{r}
pquant=quantile(faithful$eruptions,probs=c(0.25,0.5,0.75))

pquant[3]-pquant[1]   # IQR

IQR(faithful$eruptions)   # IQR 명령어

max(faithful$eruptions)-min(faithful$eruptions)   # 표본의 범위

R=range(faithful$eruptions)   # range를 벡터로 구해주는 명령어
R
R[2]-R[1]
```

## 22 : 수치 요약 
```{r}
iqr.val=IQR(faithful$eruptions)

c(pquant[1]-1.5*iqr.val, pquant[3] +1.5*iqr.val)

faithful$eruptions[faithful$eruptions > pquant[3] +1.5*iqr.val]

faithful$eruptions[faithful$eruptions < pquant[3] -1.5*iqr.val]

summary(faithful$eruptions)
```

## 23 : box plot (상자그림)
```{r}
par(mfrow=c(1,2))

boxplot(faithful$eruptions,main='Eruptions')

boxplot(faithful$waiting,main='Waiting')

ggplot(faithful) + geom_boxplot(aes(x="", y=waiting))
```

## 24 : Confidence Interval
```{r}
dev.off()

n = 49; sigma=30 ; xbar = 157.02 ; alpha=0.05 ; d=5

qnorm(1-alpha/2) # Z_(0.025)

c.i <- c(xbar - qnorm(1-alpha/2)*sigma/sqrt(n), 
         xbar + qnorm(1-alpha/2)*sigma/sqrt(n))
c.i
```

## 25 : Find P-value
```{r}
mu0=1200; sigma=100; n=25; alpha=0.05

xbar=1240; z=(xbar-mu0)/(sigma/sqrt(n))

z

z.alpha=qnorm(0.95)

z.alpha

pval=1-pnorm(z)

pval
```

## 26 : t-Test (One sample t-Test)
```{r}
bulb <- c(2000, 1975, 1900, 2000, 1950, 1850, 1950, 2100, 1975)

mean(bulb)

sd(bulb)

qt(0.95,8) 

t.test(bulb, mu=1950, alternative="greater")
```

## 27 : t-Test (paired t-Test) 
```{r}
A <- c(4.8,4.0,5.8,4.9,5.3,7.4)

B <- c(4.0,4.2,5.2,4.9,5.6,7.1)

t.test(A-B,mu=0)
```

## 28 : t-Test (Two sample t-Test : equal variance) 
```{r}
x_1 <- c(19.54, 14.47, 16.00, 24.83, 26.39, 11.49)

x_2 <- c(15.95,25.89,20.53,15.52,14.18,16.00)

# Pooled standard deviation
sqrt(((6-1)*var(x_1)+(6-1)*var(x_2))/(6+6-2)) 

# t-test procedure
t.test(x_1,x_2,var.equal=TRUE,conf.level=0.95) # t-test procedure
```

## 29 : t-Test (Two sample t-Test : not equal variance) 
```{r}
x_1 <- c(12.7,19.3,20.5,10.5,14.0,10.8,16.6,14.0,17.2)

x_2 <- c(18.2,32.9,10.0,14.3,16.2,27.6,15.7)

# t-test procedure
t.test(x_1,x_2,"less",var.equal=FALSE,conf.level=0.95) 
```

## 30 
```{r}
attach(sleep)

# t-test (paried t-test)
t.test(extra~group, paired=TRUE)

# var.test procedure
var.test(extra~group)

# t-test (two sample t-test)
t.test(extra~group, var.equal=TRUE)
```











```

